\chapter{Introduction}
\section{Motivation}
\paragraph{}The interest in positioning system has been around for many years, especially after the success of Global Positioning System based on the Global Navigation Satellite Systems (GNSS) technology that enable the outdoor positioning with less than one meter deviation in accuracy [22]. With the achievement of GPS, the next issue to be focused on is the indoor positioning. There has been some proposed approach for indoor positioning such as fingerprinting, triangulation, trilateration, etc. However, the we believed that there is still room for improvement in terms of accuracy for indoor positioning which will complement the full positioning (indoor and outdoor) system along with the use of GPS to achieve the outdoor positioning.
Our thesis proposed a real-time indoor and outdoor positioning system with an improvement in accuracy of Bluetooth Low Energy (BLE)-based indoor positioning. The aforementioned positioning system tends to result in low accuracy positioning due to BLE nature of low power consumption and the fact that other surrounding signals such as WiFi [23] and environmental factors can cause an error in signal strength measurement. Therefore, we believed that by knowing the equation of environment variable during the process of distance estimation will help improve the accuracy.



\section{Problem Descriptions}
\paragraph{}The GPS can only achieve the outdoor positioning due to its limitation. Therefore, there is the need of another technology to implement the indoor positioning. However, the BLE also have problem with accuracy when there is an obstacle or signal interference, making the target object position estimation deviate from the actual target object position.


\section{Objectives}
\paragraph{}The objective of this thesis is to research a method that can enhance the performance of indoor positioning accuracy based on device context information and showcase the visualization of the results real-time on 2-D map in smart phone device. This thesis aims to find the optimal method approach for indoor localization and provide solution for deployment. Our indoor positioning demonstration will be displayed in a 2-D map of a specified floor.
    \begin{itemize}
    	\item Explore the techniques that can improve the accuracy of BLE-based indoor positioning.
    	\item Mobile Application to show the result of indoor positioning by BLE and outdoor positioning by GPS.
    \end{itemize}


\section{Scope of work}
\paragraph{} The scope of our project regarding indoor positioning only applies to an unobstructed or free space environment and the accuracy improvement methods we propose are for BLE-based indoor positioning. Our indoor positioning  system provides a 2-D position of the target.


        	        	 

