\renewcommand{\bibname}{References}

\begin{thebibliography}{2}

\bibitem{ref:r1}
Z. C. Jean et al. A 10-gram microflyer for vision-based indoor navigation. In 2006 IEEE/RSJ International Conference on Intelligent Robots and Systems, pages 3267–3272, 2006.
\bibitem{ref:r2}
A. Abdulrahman et al. Ultra wideband indoor positioning technologies: Analysis and recent advances. Sensors (Basel), 16, 2016.
\bibitem{ref:r3}
C. Chanaphon and P. Punyanuch. Camfinder: Image-Based Indoor Positioning System.PhD thesis, King Mongkut’s Institute of Technology Ladkrabang, 2014.
\bibitem{ref:r4}
H. Andy et al. The anatomy of a context-aware application. 8:187–197, 2002.
\bibitem{ref:r5}
W. Roy. An introduction to rfid technology. IEEE Pervasive Computing, 5:25–33, 2006.
\bibitem{ref:r6}
Chunhan Lee, Yushin Chang, Gunhong Park. Indoor positioning system based on incident angles of infrared emitters. Industrial Electronics Society, 2004. IECON 2004
\bibitem{ref:r7}
M. K. Mohamed, P. Sourav, and L. Alexander. Designing simple indoor navigation system for uavs. In 2011 19th Mediterranean Conference on Control and Automation (MED), pages 1223–1228, 2011
\bibitem{ref:r8}
SEBASTIAN DÄDEBY JOAKIM HESSELGREN. A system for indoor positioning using ultra-wideband technology. Department of Computer Science and Engineering CHALMERS UNIVERSITY OF TECHNOLOGY UNIVERSITY OF GOTHENBURG Gothenburg, Sweden 2017
\bibitem{ref:r9}
Chanatip C, Chawin T, Suppakorn S, Isara A. A Pre-processing Technique for BLE-based Indoor Localization. King Mongkut’s Institute of Technology Ladkrabang	Bangkok, Thailand 2018
\bibitem{ref:r10}
Shinsuke Kajioka, Tomoya Mori, Takahiro Uchiya, Ichi Takumi and Hiroshi Matsuo, "Experiment of Indoor Position Presumption Based on RSSI of Bluetooth LE Beacon," IEEE 3rd Global Conference on Consumer Electronics (GCCE), 2014.
\bibitem{ref:r11}
J. N. S. C. Hyunwook Park, "Three-dimensional positioning system using Bluetooth low-energy beacons," International Journal of Distributed, vol. 12(10), 2016. 
\bibitem{ref:r12}
R. H. Ramsey Faragher, "Location Fingerprinting With Bluetooth Low Energy Beacons," IEEE Journal on Selected Areas in Communications, vol. 13, no. 11, pp. 2418-2428, 2015.
\bibitem{ref:r13}
A. D. Blas and D. López-de-Ipiña, "Improving trilateration for indoors localization using BLE beacons," 2017 2nd International Multidisciplinary Conference on Computer and Energy Science (SpliTech), 2017.
\bibitem{ref:r14}
G. Yanying and L. Anthony. A survey of indoor positioning systems for wireless personal networks. IEEE Communications Surveys and Tutorials, 11:13–32, 2009.
\bibitem{ref:r15}
C. David, C. Mario, and S. David de la Torre. Performance evaluation of bluetooth low energy in indoor positioning systems. Trans. Emerging Telecommunications Technologies, 25:1–10, 2014.
\bibitem{ref:r16}
J. Zhu et al. Rssi based bluetooth low energy indoor positioning. In 2014 International Conference on Indoor Positioning and Indoor Navigation (IPIN), pages 526–533, 2014.
\bibitem{ref:r17}
 F. Ramsey and H. Robert. Location fingerprinting with bluetooth low energy beacons. IEEE Journal on Selected Areas in Communications, 33, 2015.
\bibitem{ref:r18}
L. Hui, D. Houshang, B. Pat, and L. Jing. Survey of wireless indoor positioning techniques and systems. IEEE Transactions on Systems, Man, and Cybernetics, 37:1067–1078, 2007.
\bibitem{ref:r19}
C. Chanaphon and P. Punyanuch. Camfinder: Image-Based Indoor Positioning System. PhD thesis, King Mongkut’s Institute of Technology Ladkrabang, 2014.
\bibitem{ref:r20}
C. Panarat and S. D. Joko. Indoor localization system using wireless sensor networks for stationary and moving target. In 2011 8th International Conference on Information, Communications and Signal Processing, 2011.
\bibitem{ref:r21}
H. W. Fentaw and T. Kim, "Indoor localization using magnetic field anomalies and inertial measurement units based on Monte Carlo localization," 2017 Ninth International Conference on Ubiquitous and Future Networks (ICUFN), 2017.
\bibitem{ref:r22}
Navigation National Coordination Ofﬁce for Space-Based Positioning and Timing. Gps accuracy, August 2017.
\bibitem{ref:r23}
R. Faragher, R. HarleAn. Analysis of the Accuracy of Bluetooth Low Energy for Indoor Positioning Applications.

\bibitem{ref:r24}
H. J. Bae and L. Choi, Indoor Positioning System with Pedestrian Dead Reckoning and BLE Inverse Fingerprinting, November 2018

\end{thebibliography}