\renewcommand{\bibname}{References}

\begin{thebibliography}{2}

\bibitem{ref:nlp1}
Liddy, E.D. (2001) \textit{Natural Language Processing}. [On-line]. Available: \url{http://surface.syr.edu/cnlp/11/}

\bibitem{ref:nlp2}
Ed B. (2017). \textit{natural language processing (NLP)}. [On-line]. Available: \url{http://searchbusinessanalytics.techtarget.com/definition/natural-language-processing-NLP}. [13 October, 2017].

\bibitem{ref:nlp3}
\textit{AI - Natural Language Processing} [Online]. Available\url{https://www.tutorialspoint.com/artificial_intelligence/artificial_intelligence_natural_language_processing.htm}

\bibitem{ref:lex1}
Dinesh T. \textit{Lexical Analysis – Compiler Design} [Online]. Available\url{http://ecomputernotes.com/compiler-design/lexical-analysis}

\bibitem{ref:lex2}
Pavel, B. (2013). Research of lexical approach and machine learning methods for sentiment analysis.

\bibitem{ref:ATRO}
Atro V. (2009). The Oxford Handbook of Computational Linguistics, Chapter11, Part-Of-Speed tagging. 

\bibitem{ref:Helmut}
Helmut S. (1995). \textit{Improvements In Part-of-Speech Tagging With an Application To German}. [On-line]. Available: \url{http://citeseerx.ist.psu.edu/viewdoc/download;jsessionid=22ABE06B1D41BBE15F16EBA1C08A1CFF?doi=10.1.1.52.2255&rep=rep1&type=pdf}. 

\bibitem{ref:sem1}
R. Schank. (1978). \textit{Conceptual Information Processing}. [On-line]. Available: \url{https://benjamins.com/#catalog/journals/sl.2.3.11wil/details}

\bibitem{ref:textNormalize}
Caroline Brun and Caroline Hagège. 2003. Normalization and paraphrasing using symbolic methods. In Proceedings of the second international workshop on Paraphrasing - Volume 16 (PARAPHRASE '03), Vol. 16. Association for Computational Linguistics, Stroudsburg, PA, USA, 41-48. DOI: https://doi.org/10.3115/1118984.1118990

\bibitem{ref:socialTextNormalize}
Eleanor Clark, Kenji Araki, Text Normalization in Social Media: Progress, Problems and Applications for a Pre-Processing System of Casual English, In Procedia - Social and Behavioral Sciences, Volume 27, 2011, Pages 2-11, ISSN 1877-0428, https://doi.org/10.1016/j.sbspro.2011.10.577.
(http://www.sciencedirect.com/science/article/pii/S1877042811024049)
Keywords: Natural Language Processing; Machine Translation; Social Media; Twitter; Text Normalization

\bibitem{ref:twitterNormalize}
Joseph Kaufmann and Jugal Kalita. 2010. Syntactic normalization of Twitter messages. In International Conference on Natural Language Processing, Kharagpur, India.



\bibitem{ref:ml1}
A. L. Samuel (1959). \textit{Some Studies in Machine Learning Using the Game of Checkers}. [On-line]. Available \url{http://ieeexplore.ieee.org/document/5392560/?reload=true}. [13 October, 2017].

\bibitem{ref:cnnParaphase}
Wenpeng Yin, Hinrich Schutze. \textit{Convolutional Neural Network for Paraphrase Identification} [Online]. Avaliable\url{https://aclanthology.info/pdf/N/N15/N15-1091.pdf}

\bibitem{ref:fnn1}
Zell, Andreas (1994). Simulation Neuronaler Netze [Simulation of Neural Networks] (in German) (1st ed.). Addison-Wesley. p. 73. ISBN 3-89319-554-8.

\bibitem{ref:fnn2}
Jan A. Botha, Emily Pitler, Ji Ma, Anton Bakalov, Alex Salcianu, David Weiss, Ryan McDonald, Slav Petrov. (2017). Natural Language Processing with Small Feed-Forward Networks.[On-line]. Available \url{https://arxiv.org/abs/1708.00214}

\bibitem{ref:lstm1}
Olah C. (2015). Understanding LSTM Networks. [On-line] Available \url{http://colah.github.io/posts/2015-08-Understanding-LSTMs/}

\bibitem{ref:lstm1New}
Travis A. \textit{Duplicate Question Pair Detection with Deep Learning}[Online]. Avaliable\url{https://web.stanford.edu/class/cs224n/reports/2759336.pdf}

\bibitem{ref:lstm2New}
Elkhan D., Sukolsak S., Katherine Y.\textit{Quora question Duplication} [Online]. Available
\url{https://web.stanford.edu/class/cs224n/reports/2761178.pdf}

\bibitem{ref:lemma}
\url{https://nlp.stanford.edu/IR-book/html/htmledition/stemming-and-lemmatization-1.html}


\bibitem{ref:LDA}
Robinson, David. (2017). \textit{Convert Statistical Analysis Objects into Tidy Data Frames} [Online]. Available \url{https://CRAN.R-project.org/package=broom.}

\bibitem{ref:glove}
Jeffrey Pennington, Richard Socher, Christopher D. Manning. \textit{GloVe: Global Vectors for Word Representation} [Online]. Available \url{https://nlp.stanford.edu/pubs/glove.pdf}


\bibitem{ref:tfidf}
Julia S. and David R. \textit{Term Frequency and Inverse Document Frequency (tf-idf) Using Tidy Data Principles} [Online]. Available\url{https://cran.r-project.org/web/packages/tidytext/vignettes/tf_idf.html}

\bibitem{ref:fed1}
Roman V. \textit{Feed-Forward Neural Networks} [Online]. Available\url{http://www.eis.mdx.ac.uk/staffpages/rvb/teaching/BIS3226/hand11.pdf}

\bibitem{ref:w2v1}
Chris M. \textit{Word2Vec Tutorial - The Skip-Gram Model} [Online]. Available\url{http://mccormickml.com/2016/04/19/word2vec-tutorial-the-skip-gram-model/}

\bibitem{ref:w2v2}
NSS \textit{An Intuitive Understanding of Word Embeddings: From Count Vectors to Word2Vec} [Online]. Available\url{https://www.analyticsvidhya.com/blog/2017/06/word-embeddings-count-word2veec/}

\bibitem{ref:lstmMeth1}
Christopher O. \textit{Understanding LSTM Networks} [Online]. Available\url{http://colah.github.io/posts/2015-08-Understanding-LSTMs/}

\bibitem{ref:deadre}
Han Jun Bae and Lynn Choi











\end{thebibliography}